---
title: "Video"
author: "Zain"
date: "2025-03-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
library(here)
library(tidyverse)

```

```{r}

m2_main <- read.csv(here("data", "new_clean_data", "data", "reprocessed_M2_data.csv"))


video <- m2_main %>% select(
    "respondent_id", 
    "age",
    "gender.x",
    "issue",
    "increase_the_perception_of_progress_on_an_issue",
    "increase_knowledge_about_an_issue",
    "demonstrating_work_or_success_with_partners",
    "call_to_take_action_on_an_issue",
    "promote_a_brand_or_product",
    "authentic",
    "informative_factual",
    "serious",
    "optimistic_happy",
    "light.hearted_informal",
    "urgent_shocking",
    "sad_moving",
    "relatable_unifying",
    "doing_a_presentation",
    "at_an_event_or_conference",
    "in_situ_daily_life",
    "being_interviewed",
    "showing_work_being_done",
    "data_visualisation",
    "businessperson_politician_x_universal",
    "expert_scientist_x_universal",
    "influencer_celebrity_x_universal",
    "bill_gates_x_universal",
    "a_beneficiary_of_aid_x_universal",
    "parents_x_universal",
    "children_x_universal",
    "women_only_no_men_at_all_x_universal",
    "men_only_no_women_at_all_x_universal",
    "men_and_women_x_universal",
    "melinda_french_gates_x_universal",
    "a_foundation_worker_or_local_partner_x_universal",
    "text",
    "has_animation",
    "dynamic_filming",
    "unseen_narrator",
    "music",
    "close.ups",
    "seen_narrator",
    "black_and_white",
     "market"
)


write.csv(video, here("data", "clean_data", "video_variables.csv"), row.names = FALSE)

